\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-28 coqimpl.tex
Fix reorganization.

Importantly, the recursor field (e.g. "neg") is not actually inheritable, because it is not compiled like any other fields---recall how other fields are compiled into reusable pieces of (parametrized) module, a recursor field is not compiled like that. For all the children family, we have to reconstruct and override with a ``new'' recursor using the (maybe inherited) handler family. This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers (mundane fields) from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (since they only rely on ``the abstracted
interface'' module "b_3"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "ff_24"---doesn't require another type-check and is re-used during the type-checking and compilation of "B2.neg".  Of course, in the implementation, our plugin will ``inherit'' the
recursor "neg" in the surface \YZ{Show this recursor, as you do above for the recursor "Definition neg := ...".}
but what the plugin actually does is doing a second exhaustiveness
checking in children family like mentioned above, with the ``same'' motive and ``same'' handler family.\YZ{A source of confusion in this section is that the reader often has to guess who performs the actions: is it the programmer or the Coq plugin?}\EDJreply{Good idea. Let me reorgnaize this section to ``first programming interface'', then ``plugin implementation''}

>>>>

Importantly, the recursor field (e.g. "neg") is not actually inheritable, because it is not compiled like any other fields---recall how other fields are compiled into reusable pieces of (parametrized) module, a recursor field is not compiled like that. For all the children family, we have to reconstruct and override with a ``new'' recursor using the (maybe inherited) handler family. This is affordable since each recursor handler doesn't need
to be rechecked---look at "B2.neg_handler", there is only one new
handler for "uu" and the handlers (mundane fields) from the parent
"B.neg_handler.tt,B.neg_handler.ff" have already been type-checked and
inherited (since they only rely on ``the abstracted
interface'' module "b_3"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "ff_24"---doesn't require another type-check and is re-used during the type-checking and compilation of "B2.neg". For example, for the new "neg", when compiling family "B2" into a module, at the appropriate place our plugin will insert
\begin{minted}{Coq}
  Definition neg := b_rec (fun _ => b) neg_handler.tt neg_handler.ff neg_handler.uu.
\end{minted}
where "b_rec" and "b" are the corresponding recursor and the (vanilla but extended and modified) inductive type in that compiled module. Note that, even though "b_rec" and "b" has the same name as before, they are in the newly-compiled module so they refer to totally different things.

Of course, in the implementation, our plugin will ``inherit'' the
recursor "neg" in the surface \YZ{Show this recursor, as you do above for the recursor "Definition neg := ...".}\EDJreply{Added above. Please Check.}
but what the plugin actually does is doing a second exhaustiveness
checking in children family like mentioned above, with the ``same'' motive and ``same'' handler family.\YZ{A source of confusion in this section is that the reader often has to guess who performs the actions: is it the programmer or the Coq plugin?}\EDJreply{Good idea. Let me reorgnaize this section to ``first programming interface'', then ``plugin implementation''}\EDJreply{Please check.}
